---
title: "Exam3"
author: "Holt"
date: "7/9/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#setwd
setwd("C:/Users/Braden/Documents/Data Science/Exam 3")

# load packages
library(rio)
library(bit64)
library(tidyverse)
library(data.table)
library(WDI)
library(plm)
library(countrycode)
library(googlesheets4)
library(labelled)
library(varhandle)
library(ggrepel)
library(geosphere)
library(sp)
library(rgeos)
library(viridisLite)
library(viridis)
library(usethis)
library(mapview)
library(rnaturalearth)
library(rnaturalearthdata)
library(devtools)
library(rnaturalearthhires)
library(raster)
library(sf)
library(Imap)
library(ggsflabel)
library(remotes)
library(raster)
library(Rcpp)
library(shiny)
library(tidycensus)
library(XML)
library(rvest)
library(dplyr)
library(ggplot2)
library(lubridate)
library(janeaustenr)
library(stringr)
library(tidyr)
library(pdftools)
library(gutenbergr)
library(knitr)
library(ggplot2)
library(dplyr)
library(tidytext)
library(scales)
library(wordcloud)
library(topicmodels)
library(readr)

```

## Questions
1. Clear Environment
```{r, echo = TRUE}
rm(list=ls(all = TRUE))
```

1A/B. Load Data
```{r, echo = TRUE}
v10 <- get_acs(geography = "state", 
               variables = c(poverty = c("B06012_002",
                            year = 2010)))

v15 <- get_acs(geography = "state", 
               variables = c(poverty = c("B06012_002",
                                         year = 2015)))
inequality_panel <- left_join(v10, v15, by = "NAME")
```

1C. 
```{r, echo = TRUE}
setnames(inequality_panel,"estimate.x", 'gini')
setnames(inequality_panel, "estimate.y", "gini")
```

1D. 
```{r, echo = TRUE}
setnames(inequality_panel, "NAME", "state")
```

1E. 
```{r, echo = TRUE}
inequality_panel$variable.x <- 2010
inequality_panel$variable.y <- 2015
setnames(inequality_panel, "variable.x", "2010", skip_absent = TRUE)
setnames(inequality_panel, "variable.y", "2015")
```


1F. 
```{r, echo = TRUE}
head(inequality_panel)
```


8. 
```{r, echo = TRUE}
gdp_current <- WDI(country = 'all', 
                    indicator = 'NY.GDP.DEFL.ZS',
                    start = 2006,
                    end = 2007,
                    extra = FALSE,
                    cache = NULL)
```


15. 2015 is the standard for deflation (=100) 
```{r, echo = TRUE}
usd.deflator <- 
  WDI(country = 'USA', 
      indicator = 'NY.GDP.DEFL.ZS',
      start = 2015,
      end = 2015,
      extra = FALSE,
      cache = NULL)
```

10. UI, input & output; Server, functions; executable ShinyApp

11.
```{r, echo = FALSE}
armeniatext <- pdf_text(pdf = "https://pdf.usaid.gov/pdf_docs/PA00TNMG.pdf")
```


12.
```{r, echo = TRUE}
armeniatext <- as.data.frame(armeniatext, stringAsFactors = FALSE)
colnames(armeniatext)[which(names(armeniatext) == "armeniatext")] <- "text" 
```

13.
```{r, echo = TRUE}
armeniatext <- armeniatext %>% 
  unnest_tokens(word, text) %>%
  anti_join(stop_words)
```

14.
```{r, echo = TRUE}
freq <- armeniatext %>% 
  count(word, sort = TRUE)

head(freq, num = 5)
```


15.
```{r, echo = TRUE}
hot100exam <- "https://www.billboard.com/charts/hot-100"
hot100exam <- read_html(hot100exam)
```

16. 
```{r, echo = TRUE}
body_nodes <- hot100exam %>% 
  html_node("body") %>% 
  html_children
```

17.
```{r, echo = TRUE}
body_nodes <- hot100exam %>% 
  html_node("body") %>% 
  html_children

# get data 
rank <- hot100exam %>% 
  rvest::html_nodes('body') %>% 
  xml2::xml_find_all("//span[contains(@class,
                     'chart-element__rank__number')]") %>% 
  rvest::html_text()

title <- hot100exam %>% 
  rvest::html_nodes('body') %>% 
  xml2::xml_find_all("//span[contains(@class,
                     'chart-element__information__song')]") %>%
  rvest::html_text()

artist <- hot100exam %>% 
  rvest::html_nodes('body') %>% 
  xml2::xml_find_all("//span[contains(@class,
                     'chart-element__information__artist')]") %>%
  rvest::html_text()

last_week <- hot100exam %>% 
  rvest::html_nodes('body') %>% 
  xml2::xml_find_all("//span[contains(@class,
                     'chart-element__meta text--center color--secondary text--last')]") %>%
  rvest::html_text() 

# put it all together
hot100exam_df <- data.frame(rank,last_week,artist,title)